Every Author as First Author

### 2023-03-29 paper.tex
Future Work and circular arrangements

>>>>

One limitation of our new standard for listing names is that longer surnames
gain some bias.
For example, ``Olds'' (the second half of ``Mitchell-Olds'')
is clearly visible in \citet{currency-fluctuation}.
Will this lead to longer and longer academic surnames in the future?
Arguably, longer names already receive some bias without our system,
as they take up more relative space in the bibliography.
Yet in practice so far, most surnames seem to have a similar length.
The readability of a \emph{suffix} of a surname also does not seem to
bias the actual name much.

A final issue is that overlapping name stacks are not easy to read.
It may be possible to write names in a way that has no first name
but still makes all names clearly readable.
For example, a circle has no beginning or end, so arranging the names
in a circular pattern avoids arranging any author ``first''.
Figure~\ref{fig:circles} shows some initial experiments in this direction.
It remains unsolved how to fit such circular arrangements
in with the rest of a document.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/circles}
  \caption{Circular arrangements of the authors of
    \citet{LessThanEdgeMatching_JIP}.  Drawn in Inkscape
    using Circular Align and Distribute, onto a circle of
    radius 50 (left) or 200 (right); followed by $90^\circ$ rotation
    (left); and rotating $180^\circ$ to make names upright (bottom).}
  \label{fig:circles}
\end{figure}
